\thesistitle

### 2019-07-30 sections/background.tex
An example
Class level clones
OOP + AST

In this study, we use the symbols given in this table in our formulas.

@@

>>>>

A \textbf{range} denotes the line and column at which a code fragment starts and ends. In this study, we use the symbols given in this table in our formulas.

@@

\section{(Object-Oriented) Programming Languages}
In this section we describe the relevant parts of the programming languages we research and experiment on.

\subsection{AST}
An Abstract Syntax Tree (AST) is a tree consisting of an hierarchical representation of the source code of a program. Detecting code clones on the AST of a program allows for a deeper understanding of the concepts that are being analyzed. Having an AST, we know how concepts in the code are related. This helps to determine in what classes and methods cloned code is found.

Having access to a programs' AST also helps in the process of refactoring. Moving AST nodes rather than textual modifications reduces error margins because the tree structure stays intact.
